---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# augassign

<!-- badges: start -->
<!-- badges: end -->

The goal of augassign is to provide [**aug**mented **assign**ment](https://en.m.wikipedia.org/wiki/Augmented_assignment) simular to what is seen in languages such as [Python](https://docs.python.org/2.0/ref/augassign.html).

## Installation

You can install the package with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("EmilHvitfeldt/augassign")
```

This package will most likely never be put on CRAN.

## Example

The infix operators in this packages allows you to rewrite expressions such as `x <- x + 1` into `x %+=% 1`. The package contains the most common arithmatic operators.

```{r}
library(augassign)

x <- 1

x %+=% 2

x

x %-=% 1

x

x %*=% 100

x

x %/=% 20

x
```

Also works in loops

```{r}
y <- 0
for (i in 1:100) {
  y %+=% i
}

y
```

is scoped correctly to work inside functions

```{r}
x <- 1

f <- function(x) {
  x %+=% 10
  x
}

f(10)

x
```

Where augmented assignment shines is when you have long variable names or if you need to modify something deeply in a list.

```{r}
list_with_really_long_name <- list(h = list(x = 1),
                                   x = 1)

list_with_really_long_name

list_with_really_long_name$x %+=% 1

list_with_really_long_name$h$x %+=% 100

list_with_really_long_name
```

Since the package is rewriting the expressions under the hood, you are able to work with vectors just as easy as single numbers

```{r}
x <- 1:10

x %+=% x

x
```

# Downsides

The mayor downside is that these operators are vastly slower then the traditional counterparts

```{r}
x <- 0
bench::mark(check = FALSE,
  {x <- x + 1},
  {x %+=% 1}
)
```

Due the orders of operations, it is not possible to chain together multiple operators.

```{r, error=TRUE}
a <- b <- c <- 1

a %+=% b %+=% c
```

